---
title: "Country Analysis"
---

This page will explore all 3 metrics of life expectancy, population, and GDP per capita for Canada from 1952-2007.

```{r}
gapminder <- read.csv("./gapminder.csv")
pacman::p_load(tidyverse)
canada <- gapminder[gapminder$country=="Canada",]
```

## Canadian GDP per Capita by Year
```{r}
ggplot(data=canada)+
geom_col(mapping = aes(x=year, y=gdp_per_capita), fill = "green")+
labs(title = "Canadian GDP per Capita from 1952-2007", x = "Year", y="GDP per Capita")
```

## Canadian Population by Year
```{r}
ggplot(data=canada)+
geom_col(mapping = aes(x=year, y=population_millions), fill = "red")+
labs(title = "Canadian Population from 1952-2007", x = "Year", y="Population (millions)")
```

## Canadian Life Expectancy by Year
```{r}
ggplot(data=canada)+
geom_col(mapping = aes(x=year, y=life_expectancy), fill = "blue")+
labs(title = "Canadian Life Expectancy from 1952-2007", x = "Year", y="Life Expectancy (years)")
```

We see that all 3 metrics, GDP per capita, population, and life expectancy, steadily increase throughout 1952-2007. GDP per capita has over tripled and population has over doubled, while life expectancy seems to have increased around 20%.